\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/introduction.tex
Update

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

@@

    \item We conducted multiple experiments and a user study to validate the
	usability and effectiveness of \tool.  We also proposed several
	countermeasures for our attack model, which are reasonable and
	insightful. 
	%\fengwei{Add countermeasures, in particular the isolation design.}
	%\shuqing{Isolated UI rendering is added in the last paragraph.}
\end{itemize}

>>>>

Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Fully Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  
We conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a case study for attacks in
sharing power banks, one of the application scenarios of \tool.  
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

@@

    \item We conducted a case study and multiple experiments to validate the
	usability and effectiveness of \tool.  We also proposed several
	countermeasures for our attack model, which are reasonable and
	insightful. 
	%\fengwei{Add countermeasures, in particular the isolation design.}
	%\shuqing{Isolated UI rendering is added in the last paragraph.}
\end{itemize}
